Meta-analysis

### 2019-09-14 04_Prep_data.Rmd
Reformat R code

for(i in levels(as.factor(PM_MB_means$Trial_ref))){
   dat1 <- PM_MB_means[PM_MB_means$Trial_ref == i,]

   if(any(is.na(unique(dat1$row_spacing)))){
      warning(paste(unique(dat1$Trial_ref), "at", unique(dat1$Location), "in year", unique(dat1$Year), "has unknown row.spacing (NA)\n 'yield_gain' and 'proportional yield gain' not calculated\n") )
      next()}

   for(j in unique(dat1$row_spacing)){

      dat2 <- dat1[dat1$row_spacing == j,]
      controlY <- mean(dat2[dat2$Fungicide == "control","grain_yield.t.ha."])

      dat2$yield_gain <- dat2$grain_yield.t.ha. - controlY
      dat2$prop_YG <- dat2$yield_gain/controlY

      dat2[dat2$Fungicide == "control",c("yield_gain", "prop_YG")] <- NA

      dat1[dat1$row_spacing == j,] <- dat2
   }
   PM_MB_means[PM_MB_means$Trial_ref == i,] <- dat1
}

# caluculate yield gain and prop_yield gain for experiments with no row spacing data
dat1 <- PM_MB_means[PM_MB_means$Trial_ref == "AM1303",]
controlY <- mean(dat1[dat1$Fungicide == "control","grain_yield.t.ha."])
dat1$yield_gain <- dat1$grain_yield.t.ha. - controlY
dat1$prop_YG <- dat1$yield_gain/controlY
dat1[dat1$Fungicide == "control",c("yield_gain", "prop_YG")] <- NA
PM_MB_means[PM_MB_means$Trial_ref == "AM1303",] <- dat1

write.csv(PM_MB_means, "data/1902 powdery mildew-Mungbean - Collated means.csv")

>>>>

for (i in levels(as.factor(PM_MB_means$Trial_ref))) {
   dat1 <- PM_MB_means[PM_MB_means$Trial_ref == i, ]

   if (any(is.na(unique(dat1$row_spacing)))) {
      warning(
         paste(
            unique(dat1$Trial_ref),
            "at",
            unique(dat1$Location),
            "in year",
            unique(dat1$Year),
            "has unknown row.spacing (NA)\n 'yield_gain' and 'proportional yield gain' not calculated\n"
         )
      )
      next()
   }

   for (j in unique(dat1$row_spacing)) {
      dat2 <- dat1[dat1$row_spacing == j, ]
      controlY <-
         mean(dat2[dat2$Fungicide == "control", "grain_yield.t.ha."])

      dat2$yield_gain <- dat2$grain_yield.t.ha. - controlY
      dat2$prop_YG <- dat2$yield_gain  /  controlY

      dat2[dat2$Fungicide == "control", c("yield_gain", "prop_YG")] <-
         NA

      dat1[dat1$row_spacing == j, ] <- dat2
   }
   PM_MB_means[PM_MB_means$Trial_ref == i, ] <- dat1
}

# caluculate yield gain and prop_yield gain for experiments with no row spacing data
dat1 <- PM_MB_means[PM_MB_means$Trial_ref == "AM1303", ]
controlY <-
   mean(dat1[dat1$Fungicide == "control", "grain_yield.t.ha."])
dat1$yield_gain <- dat1$grain_yield.t.ha. - controlY
dat1$prop_YG <- dat1$yield_gain / controlY
dat1[dat1$Fungicide == "control", c("yield_gain", "prop_YG")] <- NA
PM_MB_means[PM_MB_means$Trial_ref == "AM1303", ] <- dat1

write.csv(PM_MB_means,
          "data/1902 powdery mildew-Mungbean - Collated means.csv")
```
